---
title: "Linearmodel"
author: "Amee Rodrick"
date: "11/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
dataF <- read.csv(file="http://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)

```


## Now with ggplot - first select the basic data

```{r}
basicNN <- ggplot(dataF,aes(y=SIMS,x=ARM))
```
## Now add in scatterplot

```{r}
basicNN + geom_point()+ geom_smooth(method=lm)
```

```{r}
basicNN <- ggplot(dataF,aes(y=SIMS,x=GRIP))
```
## Now add in scatterplot

```{r}
basicNN + geom_point()+ geom_smooth(method=lm)
```

```{r}
model.1 <- lm(SIMS~ARM,data=dataF)
summary.lm(model.1)
```


```{r}
new <- data.frame(ARM=88,GRIP=94)
predict.lm(model.1,new)
predict(model.1,new,interval="prediction")
```



This particular model about 47% of the variation more then the mean model did. The Adjusted R squared is 0.467

```{r}
model.2 <- lm(SIMS~GRIP,data=dataF)
summary.lm(model.2)
``` 

```{r}
new <- data.frame(ARM=88,GRIP=94)
predict.lm(model.2,new)
predict(model.2,new,interval="prediction")
```

The model for ARM is a independent model and is lower then model.1 by 20% at 0.5361543



```{r}
model.3 <- lm(SIMS~GRIP + ARM,data=dataF)
summary.lm(model.3)
``` 

```{r}
new <- data.frame(ARM=88,GRIP=94)
predict.lm(model.3,new)
predict(model.3,new,interval="prediction")
```
  
In this model.3 the Adjusted R square is 0.5358, Which makes model.3 the best model out of all three models. 


```{r}
anova(model.1,model.3)
```

This model of all three SIMS, GRIP, AND ARM are less at 217.88 then model 2 is at 188.43 meaning the ARM alone is highest model. 




